Rising from the Ashes II: Can Bar Formation Lead to Abundance Bimodalities?

### 2024-10-07 paper/ms.tex
Add summary table

@@

We select subhalo 172175 (the ID at snapshot 40) for its resemblance to the Milky Way. We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99). We refer to this subhalo as our subhalo of interest (SoI). \red{Add some morphological details of gal here}

>>>>

\newcommand{\rhalf}{\ensuremath{r_{\star,\textrm{half}}}}

@@

\begin{table}[]
  \centering
  \begin{tabular}{ll}
  \multicolumn{2}{c}{dark matter}                                                                  \\ \hline
  \multicolumn{1}{l|}{$M_{200}$}                                      & $4.97\times10^{12}\,\Msun$ \\
  \multicolumn{1}{l|}{$R_{200}$}                                      & $532\,\kpc$                \\
                                                                      &                            \\
  \multicolumn{2}{c}{baryons}                                                                      \\ \hline
  \multicolumn{1}{l|}{$\rhalf$}                                       & $2\,\kpc$                  \\
  \multicolumn{1}{l|}{$M_{\textrm{star}}(r<4\rhalf)$}                 & $7.6\times10^{12}\,\Msun$  \\
  \multicolumn{1}{l|}{$M_{\textrm{gas}}(r<4\rhalf)$}                  & $2.6\times10^{11}\,\Msun$  \\
  \multicolumn{1}{l|}{$\textrm{SFR}$}                                 & $0.56\,\Msunyr$            \\
  \multicolumn{1}{l|}{$M_{\textrm{BH}}$}                              & $2.9\times10^{8}\,\Msun$   \\
  \multicolumn{1}{l|}{$\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{Edd}}$} & $4.5\times10^{-5}$        
  \end{tabular}
  \caption{Summary statistics of our subhalo of interest at $z=0$. $M_{200}$ and $R_{200}$ are relative to the mean density of the universe, the SFR is for all gas bound to the subhalo, and the BH refers to the central BH.}
  \label{tab:summ}
\end{table}

We select subhalo 172175 (the ID at snapshot 40) for its resemblance to the Milky Way. We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99). A summary of its key properties is given in Table~\ref{tab:summ}. We refer to this subhalo as our subhalo of interest (SoI).
